---
title: "R Script Documentation"
author: "BDA400 TALHA ALI"
date: "`r Sys.Date()`"
output: html_document
---

# Purpose

This document explains a single R analysis workflow and demonstrates how an R script can be documented with clear Markdown headings, code blocks, inputs, and outputs.

## Inputs

The example uses a small synthetic dataset created directly in the R document. It contains a category field and a numeric value field.

## Outputs

The workflow:

- Displays the synthetic data.
- Calculates the mean of the numeric values.
- Creates a simple summary table.
- Demonstrates a reproducible R analysis structure.

## Example Code

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)

data <- tibble(
  category = c("A", "B", "C", "D"),
  value = c(12, 18, 15, 20)
)

data
```

## Summary Calculation

```{r summary}
mean_value <- mean(data$value)
mean_value
```

The mean is calculated directly by R from the synthetic values in the dataset.

## Verification

The code and document structure should be previewed or knitted in RStudio/Posit Cloud. The Markdown headings, code chunks, and generated output should be checked for correct rendering.

## Reproducibility

The example does not depend on personal or confidential information. The dataset is created in the document, making the example reproducible when the R Markdown file is knitted.

## AI Assistance Declaration

AI Assistance Declaration: I used ChatGPT for documentation structure, Markdown formatting, and wording suggestions. Prompts used included requests for README sections, Markdown formatting, R Markdown organization, and syntax validation. I verified the structure and code manually by reviewing the Markdown and R code. All final calculations are done by myself. I am responsible for the accuracy and originality of this work.
